Plant Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2022-11-11 script/manuscript_MEE.Rmd
a few more references and appendix table for predictors

Species abiotic niche predictors were 26 variables at 30m resolution, for linear regression models these predictors underwent both vifstep (theta = 10, max observations = 12,500) and vifcor (theta = 0.7, max observations = 12,500), and collinear features were removed leaving 16 variables (@usdm2014) (*APPENDIX 6*).

@@

To estimate the duration of dates in which plant species were flowering Weibull estimates of all spatially modelled taxa were developed (@belitz2020accuracy). Only BIEN records which occurred in the Omernik Level 4 Ecoregions within 15km of the study area (n = 5, or conditionally 6 if enough records not be found in the nearest 5), and which were from herbarium records were included. To remove temporally irrelevant herbarium records, i.e. material collected during times which flowering is impossible at the study area due to snow cover, the SnowUS dataset (@iler2021conceptual, @tran2019cloud) from 2000-2017 was analyzed for the first three days of contiguous snow absence, and the first three days of contiguous snow cover in Fall. Herbarium records after the 3rd quantile for melt, and the 1st quantile for snow cover of these metrics were removed. Species with > 10 records had their weibull distributions estimated for the date when 10% of individuals had begun flowering, when 50% were flowering, and when 90% of individuals had flowered.

@@

>>>>

Species abiotic niche predictors were 26 variables at 30m resolution, six related to climate,  five soil, four topographic, four related to cloud cover, with the remaining ... (@wilson2016remotely, @wang2016locally, @hengl2017soilgrids250m, @robinson2014earthenv) (*APPENDIX 6*). For linear regression models these predictors underwent both vifstep (theta = 10, max observations = 12,500) and vifcor (theta = 0.7, max observations = 12,500), and collinear features were removed leaving 16 variables (@usdm2014).

@@

To estimate the duration of dates in which plant species were flowering Weibull estimates of all spatially modelled taxa were developed (@belitz2020accuracy, @pearse2017statistical). Only BIEN records which occurred in the Omernik Level 4 Ecoregions within 15km of the study area (n = 5, or conditionally 6 if enough records not be found in the nearest 5), and which were from herbarium records were included. To remove temporally irrelevant herbarium records, i.e. material collected during times which flowering is impossible at the study area due to snow cover, the SnowUS dataset (@iler2021conceptual, @tran2019cloud) from 2000-2017 was analyzed for the first three days of contiguous snow absence, and the first three days of contiguous snow cover in Fall. Herbarium records after the 3rd quantile for melt, and the 1st quantile for snow cover of these metrics were removed. Species with > 10 records had their weibull distributions estimated for the date when 10% of individuals had begun flowering, when 50% were flowering, and when 90% of individuals had flowered.

@@

Layer                   Description                            Source
----    ----------------------------------------------  ---------------------
1.             Mean annual cloudiness - MODIS            Wilson et al. 2016
2.           Cloudiness seasonality 1 - MODIS            Wilson et al. 2016 
3.           Cloudiness seasonality 2 - MODIS            Wilson et al. 2016 
4.           Cloudiness seasonality 3 - MODIS            Wilson et al. 2016
5.          Beginning of the frost-free period               Wang et al.
6.             Climatic moisture deficit                     Wang et al.
7.             Degree-days above 5C from                     Wang et al.
8.             Mean annual precipitation                     Wang et al.
9.          Mean annual precipitation as snow                Wang et al.
10.             Temperature seasonality                      Wang et al.
11.       2015 Percent Grass/Herbaceous cover - MODIS         (MOD44B)
12.      2015 Percent Tree cover from Landsat 7/8              (GLCF)
13.       Soil probability of bedrock (R Horizon)             SoilGrids
14.         Soil organic carbon (Tonnes / ha)  
15.              Surface soil pH in H2O 
16.             Surface soil percent sand 
17.                    Soil USDA class                        SoilGrids
18.                Topographic elevation                    EarthEnv DEM
19.          Topographic elevation, moving window.
20.            Topographic percent slope                    EarthEnv DEM 
21.            Topographic wetness index                    EarthEnv DEM 
22.        Topographic aspect from EarthEnv DEM
23.      Annual potential solar radiation computed             r.sun.
24.       Estimated actual (w/-cloud) solar radiation
25.       Log-transformed distance to surface water   Global Surface Water Explorer
26.             Percent surface water from            Global Surface Water Explorer 
----    ----------------------------------------------  ---------------------
